Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-19 paper/v2.0/sections/appendix_a.tex
Correction appA

     + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')

@@

Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we derive the solution for Eq.~(\ref{eq:a11}) as
\begin{equation} \label{eq:a19}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
\end{equation}
Subtitling solutions in Eq.~(\ref{eq:a18}) back in Eq.~(\ref{eq:a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time-dependent Schrödinger equation Eq.~(\ref{eq:a4}) as follows
\begin{equation} \label{eq:a20}
  \begin{aligned}
    \psi_{n,m}&(x,y,t) \\
    &=  \frac{1}{\sqrt{L_x}}
    \chi_n\left(y - y_0 - \zeta(t)\right)\\
    &\quad\times
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \epsilon_nt
    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)\\
    & \quad\quad+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}

>>>>

     + \int_0^{t}L(\zeta,\dot{\zeta},t') dt'

@@

Finally, we consider our scenario where we can assume that $S(t) = eE\sin(\omega t)$, and we can derive the solution for Eq.~(\ref{eq:a11}) as
\begin{equation} \label{eq:a19}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
\end{equation}
Substituting solutions given in Eq.~(\ref{eq:a18}) back in Eq.~(\ref{eq:a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time-dependent Schrödinger equation Eq.~(\ref{eq:a4}) as follows
\begin{equation} \label{eq:a20}
  \begin{aligned}
    &\psi_{n,m}(x,y,t) \\
    & \quad=  \frac{1}{\sqrt{L_x}}
    \chi_n\left(y - y_0 - \zeta(t)\right)\\
    &\qquad\times
    \text{exp}\left(
    \frac{i}{\hbar}
    \left\{- \epsilon_nt
    + p_x x
    + \frac{eE(y - y_0)}{\omega}\cos(\omega t) \right. \right. \\
    & \left. \left. \qquad\qquad +
    m_e\left[y - y_0 -\zeta(t)\right] \dot{\zeta}(t)+
    \int_0^{t}L(\zeta,\dot{\zeta},t') dt'
    \right\}
    \right).
  \end{aligned}
\end{equation}
